Let's Get Movin': Frontiers of Optimal Transport

### 2018-05-05 reports/paper/paper.tex
Fix edits

Recent advances in machine learning points towards the versatility of genetic
 algorithms, even as a competitive alternative to deep learning based on
 gradient methods \cite{such2017deep}. Inspired by these advances, we consider
 the following genetic algorithm

@@

The applications of the optimal transport problem to the physical transportation
of objects is practically explicit in the problem statement. This is but one of
many applications, though. In particular, we explore the use of optimal
transport in the image processing of MNIST images.

@@

Optimal transport provides a natural language with which to talk about image
similarity. If we consider the darkness of a pixel as ``mass,''  the similarity
of two images could be quantified as the units of mass times distance that need
to be moved in order to transform it into the second image. This requires us to
normalize the image such that the pixel intensities sum to 1, but this is not a
problem with MNIST images which do not differ significantly in their average
brightness. The transport also requires a choice of cost function between two
pixels. We opt for an $L^2$ penalization on the distance between the pixels, but
alternative metrics such as $L^1$ perform similarly \cref{fig:mnisttransport}
illustrates what this transformation looks like for a ``0'' being transported
into a ``6.''

@@

To conclude, our goals in surveying the topics presented are two-fold. Firstly,
we hope to illustrate the richness of the computational toolkit appropriate for
solving optimal transport problems. We survey both exact methods, such as the LP
formulation and the Hungarian method, as well as potentially faster inexact
approximations, such as the entropic regularized problem and genetic algorithms.
In doing so, we emphasize both theory and empirics to understand how these
algorithms perform from different perspectives.

>>>>

Recent advances in machine learning points towards the versatility of genetic
 algorithms, even as a competitive alternative to deep learning based on
 gradient methods \cite{such2017deep}. Inspired by these advances, we consider
 the following genetic algorithm.

@@

The applications of the optimal transport problem to the physical transportation
of objects is practically explicit in the problem statement. As we highlight
previously his is but one of many applications. In particular, we explore the
use of optimal transport in the image processing of MNIST images.

@@

Optimal transport provides a natural language with which to talk about image
similarity. If we consider the darkness of a pixel as ``mass,''  the similarity
of two images could be quantified as the units of mass times distance that need
to be moved, in order to transform it into the second image. This requires us to
normalize the image such that the pixel intensities sum to 1, but this is not a
problem with MNIST images, which do not differ significantly in their average
brightness. The transport also requires a choice of cost function between two
pixels. We opt for an $L^2$ penalization on the distance between the pixels, but
alternative metrics such as $L^1$ perform similarly. \cref{fig:mnisttransport}
illustrates what this transformation looks like for a ``0'' being transported
into a ``6.''

@@

To conclude, our goals in surveying the topics presented are two-fold. Firstly,
we hope to illustrate the richness of the computational toolkit appropriate for
solving optimal transport problems. We survey both exact methods, such as the LP
formulation and the Hungarian method, as well as potentially faster inexact
approximations, such as the \eqref{eq:entropic} problem and genetic algorithms.
In doing so, we emphasize both theory and empirics to understand how these
algorithms perform from different perspectives.
